TrueSkill Through Time: the \proglang{Python} Package

### 2020-07-20 article.tex
Paper TTT: agregando ejemplos

\usepackage{bm} % \bm{\alpha} bold greek symbol
\usepackage[makeroom]{cancel} % \cancel{} \bcancel{} etc
\usepackage{wrapfig} % \begin{wrapfigure} Pone figura al lado del texto
\usepackage{mdframed}
\usepackage{algorithm}
%\usepackage{quoting}
\usepackage{mathtools}	
\usepackage{tikz}

\input{tikzlibrarybayesnet.code.tex}

@@

\begin{document}

@@

\begin{leftbar}
For code input and output, the style files provide dedicated environments.
Either the ``agnostic'' \verb|{CodeInput}| and \verb|{CodeOutput}| can be used
or, equivalently, the environments \verb|{Sinput}| and \verb|{Soutput}| as
produced by \fct{Sweave} or \pkg{knitr} when using the \code{render_sweave()}
hook. Please make sure that all code is properly spaced, e.g., using
\code{y = a + b * x} and \emph{not} \code{y=a+b*x}. Moreover, code input should
use ``the usual'' command prompt in the respective software system. For
\proglang{R} code, the prompt \code{"R> "} should be used with \code{"+  "} as
the continuation prompt. Generally, comments within the code chunks should be
avoided -- and made in the regular {\LaTeX} text instead. Finally, empty lines
before and after code input/output should be avoided (see above).
\end{leftbar}

>>>>

\usepackage{bm} % \bm{\alpha} bold greek symbol
\usepackage[makeroom]{cancel} % \cancel{} \bcancel{} etc
\usepackage{wrapfig} % \begin{wrapfigure} Pone figura al lado del texto
\usepackage{mdframed}
\usepackage{algorithm}
%\usepackage{quoting}
\usepackage{mathtools}	
\usepackage{tikz}
\usepackage{listings}
\input{tikzlibrarybayesnet.code.tex}

@@

\begin{document}
\lstset{language=Python}

@@

\begin{leftbar}
For code input and output, the style files provide dedicated environments.
Either the ``agnostic'' \verb|{CodeInput}| and \verb|{CodeOutput}| can be used
or, equivalently, the environments \verb|{Sinput}| and \verb|{Soutput}| as
produced by \fct{Sweave} or \pkg{knitr} when using the \code{render_sweave()}
hook. Please make sure that all code is properly spaced, e.g., using
\code{y = a + b * x} and \emph{not} \code{y=a+b*x}. Moreover, code input should
use ``the usual'' command prompt in the respective software system. For
\proglang{R} code, the prompt \code{"R> "} should be used with \code{"+  "} as
the continuation prompt. Generally, comments within the code chunks should be
avoided -- and made in the regular {\LaTeX} text instead. Finally, empty lines
before and after code input/output should be avoided (see above).
\end{leftbar}
In this section its show some applications of \textbf{TTT} in three(?) examples.

For each example,
the model of interest is specified, and code snippets are provided. In addition to the module
\textbf{TTT}, the libraries collections, dateutil and mathematics(Gaussian) are also required.

\subsection{Example 1: Trueskill 1vs1}

\begin{lstlisting}
	\lstinputlisting{./code/Example0.py}
\end{lstlisting}
\subsection{Example 2: Trueskill dataset}
\begin{table}[]
	\centering
	%\resizebox{\textwidth}{!}{%
		\begin{tabular}{llll}
			\hline
			Id  & Player1        & Player2        & Result \\ \hline
			101 & 'matt64'       & 'Chuk'         & 1      \\
			102 & 'matt64'       & 'David'        & 1      \\
			103 & 'ggg'          & 'matt64'       & 0      \\
			104 & 'Chuk'         & 'David'        & 0      \\
			105 & 'ggg'          & 'TheProffesor' & 0      \\
			106 & 'ggg'          & 'matt64'       & 1      \\
			107 & 'Chuk'         & 'TheProffesor' & 0      \\
			108 & 'Chuk'         & 'NaT'          & 1      \\
			109 & 'David'        & 'TheProffesor' & 1      \\
			110 & 'David'        & 'Chuk'         & 0      \\
			111 & 'TheProffesor' & 'Chuk'         & 0      \\
			112 & 'Mona'         & 'matt64'       & 1      \\
			113 & 'TiNi'         & 'David'        & 1      \\
			113 & 'Chuk'         & 'matt64'       & 1      \\
			115 & 'ggg'          & 'matt64'       & 1      \\ \hline
		\end{tabular}%
	%}
	\caption{}
	\label{tab:my-table}
\end{table}
\subsection{Example 3: Trueskill True Time}
